Random Forest to find the top important features

### 2019-10-31 scripts/15_RF_find_top_features.Rmd
update

---
title: "Random Forest to find the top important features"
author: "Anqi Dai"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
---

@@

### Use only the toxicity as the response variable

@@

### Use all of the variables in the pheno table to do RF

@@

### Removing some not expressive features

@@

No improvements at all.

@@

```{r}
top_feature <- importance(combined_tox_RF_fil, type=1, scale = F) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = 'species') %>% 
  arrange(desc(MeanDecreaseAccuracy))

top_feature
```

Although Clostridium innocuum are often present and harmless in healthy people, they have been isolated in various infections and predominantly in patients that are immunocompromised as an opportunistic bacteria.

>>>>

---
title: "Random Forest to find the top important features"
author: "Anqi Dai"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3

---

@@

### Use all features as predictors

@@

### Use all features + all pheno var as predictors

@@

### Use more abundant features(species abundance > 1%) + all pheno var as predictors

@@

No improvements at all. I think because the relatively small sample size and uneven distribution of the groups.

@@

Using the third table predictors.

```{r}
# repeat the RF M = 100 times
# pull top 10 features
N <- 10
M <- 100 
pull_top_features <- function(){
  importance(randomForest(formula = Toxicity ~ ., data = combined_fil,  importance = T ) , type=1, scale = F) %>% 
    as.data.frame() %>% 
    rownames_to_column(var = 'species') %>% 
    arrange(desc(MeanDecreaseAccuracy)) %>% 
    top_n(N) %>% 
    pull(species)
}

res <- replicate(M, pull_top_features())

stable_top_fea <- table(res) %>% 
  as.data.frame() %>% 
  rename(species = names(.)[1]) %>% 
  arrange(desc(Freq))

stable_top_fea %>% 
  kable(caption = 'Frequency of features shown as top 10 in 100 random forest runs') %>% 
  kable_styling(full_width = F, position = 'left')

```

What's interesting is this species *Ruminococcus gnavus*. [This recent paper](https://www.pnas.org/content/116/26/12672) points out that *Ruminococcus gnavus* produces a polysaccharide molecule that induces the production of inflammatory cytokines, which could be hypothesized to cause toxicity too.
